### 2015-04-06 intro.tex
edits
Incorporated new edits
Use correct class file for the camera ready version. Remove vertical space adjustments.

To address these issues, we describe \name, a declarative programming model and
implementation for eventually consistent geo-distributed data stores. The key
novelty of \name is an expressive \emph{contract language} to declare and
verify fine-grained application-level consistency properties. The programmer
uses the contract language to axiomatically specify the set of legal executions
allowed over the replicated data type. Contracts are constructed using
primitive consistency relations such as \emph{visibility} and \emph{session
order} along with standard logical and relational operators. A \emph{contract
enforcement system} statically maps operations over the datatype to a
particular consistency level available on the store, and provably validates the
correctness of the mapping. The paper makes the following contributions:
\vspace*{-.4em}
\begin{itemize}
\setlength{\itemsep}{2pt}
\item We introduce \name, a shallow extension of Haskell that supports the
	description and validation of replicated data types found on eventually
	consistent stores. Contracts are used to specify fine-grained
	application-level consistency properties, and are statically analyzed to
	assign the most efficient and sound store consistency level to the
	corresponding operation.
\item \name supports coordination-free transactions over arbitrary datatypes.
	We extend our contract language to express fine-grained transaction isolation
	guarantees, and utilize the contract enforcement system to automatically
	assign the correct isolation level for a transaction.
\item We provide meta-theory that certifies the soundness of our contract
	enforcement system, and ensures that an operation is only executed if the
	required conditions on consistency are met.
\item An implementation of \name as a transparent shim layer over
	Cassandra~\cite{Cassandra}, a well-known general-purpose data store.
	Experimental evaluation over a set of real-world applications, including a
	Twitter-like micro-blogging site and an eBay-like auction site illustrates
	the practicality of our approach.
\end{itemize}

\noindent The rest of the paper is organized as follows. The next section describes the
system model.  We describe the challenges in programming with eventually
consistent data stores, and introduce \name\ contracts as a proposed solution
to overcome these issues in \S~\ref{sec:motivation}. \S~\ref{sec:lang} provides
more details on the contract language, and its mapping to the store consistency
levels, along with meta-theory for certifying the correctness of the mapping.
\S~\ref{sec:txns} introduces transaction contracts and their classification.
\S~\ref{sec:impl} describes the implementation and provides details about the
optimizations needed to make the system practical. \S~\ref{sec:results}
discusses experimental evaluation. \S~\ref{sec:related} and~\ref{sec:concl}
present related work and conclusions.

>>>>

To address these issues, we describe \name, a declarative programming model and
implementation for \ecds. The key
novelty of \name is an expressive \emph{contract language} to declare and
verify fine-grained application-level consistency properties. The programmer
uses the contract language to axiomatically specify the set of legal executions
allowed over the replicated data type. Contracts are constructed using
primitive consistency relations such as \emph{visibility} and \emph{session
order} along with standard logical and relational operators. A \emph{contract
enforcement system} statically maps operations over the datatype to a
particular consistency level available on the store, and provably validates the
correctness of the mapping. The paper makes the following contributions:

\begin{itemize}[noitemsep]
\item We introduce \name, a shallow extension of Haskell that supports the
	description and validation of replicated data types found on \ecds. Contracts
	are used to specify fine-grained application-level consistency properties,
	and are statically analyzed to assign the most efficient and sound store
	consistency level to the corresponding operation.
\item \name supports coordination-free transactions over arbitrary datatypes.
	We extend our contract language to express fine-grained transaction isolation
	guarantees, and utilize the contract enforcement system to automatically
	assign the correct isolation level for a transaction.
\item We provide meta-theory that certifies the soundness of our contract
	enforcement system, and ensures that an operation is only executed if the
	required conditions on consistency are met.
\item An implementation of \name as a transparent shim layer over
	Cassandra~\cite{Cassandra}, a well-known general-purpose data store.
	Experimental evaluation over a set of real-world applications, including a
	Twitter-like micro-blogging site and an eBay-like auction site illustrates
	the practicality of our approach.
\end{itemize}

\noindent The rest of the paper is organized as follows. The next section
describes the system model.  We describe the challenges in programming under
eventual consistency, and introduce \name\ contracts as a proposed solution to
overcome these issues in \S~\ref{sec:motivation}. \S~\ref{sec:lang} provides
more details on the contract language, and its mapping to the store consistency
levels, along with meta-theory for certifying the correctness of the mapping.
\S~\ref{sec:txns} introduces transaction contracts and their classification.
\S~\ref{sec:impl} describes the implementation of \name on top of Cassandra.
\S~\ref{sec:results} discusses experimental evaluation. \S~\ref{sec:related}
and~\ref{sec:concl} present related work and conclusions.
